\textbf{Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-09 ms.tex
tweaks
better caption for fig 8

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region.
The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.

@@

@@

 % Notebook: Figure-DECam-CMD
 \begin{figure}
 \centering
 \includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
 \caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
 Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
 \label{fig:decam-field}
 \end{figure}

% Notebook: Figure-DECam-CMD
\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

% Notebook: Proper-motion-membership
\begin{figure*}[ht!]
\centering
\includegraphics[width=\textwidth]{figures/pm-model.pdf}
\caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
The circles show the regions used as cluster and control fields in the proper motion inference (\sectionname~\ref{sec:pmclean}).
The control fields, together, have the same area as the cluster field.
\textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
The clear over-density in the cluster field (blue) are stars in \clustername.}
\label{fig:pm-members}
\end{figure*}

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ r | l | l}
        \toprule
        Parameter & Value & Description \\
        \tableline
        $\mean{\alpha}$ & $178.8^\circ$ & mean right ascension \\
        $\mean{\delta}$ & $-29.4^\circ$ & mean declination \\
        $\mean{D}$ & $29~\kpc$ & mean Heliocentric distance \\
        $\mean{\mu_\alpha}$ & $-0.56~\masyr$ & mean proper motion in RA\\
        $\mean{\mu_\delta}$ & $0.47~\masyr$ & mean proper motion in Dec\\
        \tableline
        $\tau$ & $130~\textrm{Myr}$ & age \\
        $M$ & $1200~\msun$ & total stellar mass \\
        $\feh$ & $-1.1$ & metallicity \\
        \tableline
        $A_V$ & $0.3$ & extinction \\
        \toprule
    \end{tabular}
\caption{Inferred properties of \clustername.
\label{tbl:clusterparams}}
\end{center}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
\caption{The position-velocity diagram of GASS Gaussian centers.}
\label{fig:gasspv}
\end{figure}

@@

>>>>

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region:
The left panel shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}.
Surprisingly, this group appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.

@@

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
\label{fig:decam-field}
\end{figure}

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

@@

% Notebook: Proper-motion-membership
\begin{figure*}[t!]
\centering
\includegraphics[width=0.9\textwidth]{figures/pm-model.pdf}
\caption{\textbf{Left panel}: Sky positions of all \gaia\ sources in this region with $\bprp < 0.35$ (grey markers).
The circles show the regions used as cluster and control fields in the proper motion inference (\sectionname~\ref{sec:pmclean}).
The control fields, together, have the same area as the cluster field.
\textbf{Right panel}: The colored 2D density shows the difference in number of sources per pixel in the cluster field versus the two control fields (see left panel).
The clear over-density in the cluster field (blue) are stars in \clustername.}
\label{fig:pm-members}
\end{figure*}

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ r | l | l}
        \multicolumn{3}{c}{\textbf{Inferred properties of \clustername}} \\
        \toprule
        Parameter & Value & Description \\
        \tableline
        $\mean{\alpha}$ & $178.8^\circ$ & mean right ascension \\
        $\mean{\delta}$ & $-29.4^\circ$ & mean declination \\
        $\mean{D}$ & $29~\kpc$ & mean Heliocentric distance \\
        $\mean{\mu_\alpha}$ & $-0.56~\masyr$ & mean proper motion in RA\\
        $\mean{\mu_\delta}$ & $0.47~\masyr$ & mean proper motion in Dec\\
        \tableline
        $\tau$ & $130~\textrm{Myr}$ & age \\
        $M$ & $1200~\msun$ & total stellar mass \\
        $\feh$ & $-1.1$ & metallicity \\
        \tableline
        $A_V$ & $0.3$ & extinction \\
        \toprule
    \end{tabular}
\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
\label{tbl:clusterparams}}
\end{center}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=8cm]{figures/gass_vlsrmlon.pdf}
\caption{The position-velocity diagram of GASS \hi Gaussian centers in the same region as \figurename~\ref{fig:gass_maps}, showing the line-of-sight velocity (in the local standard of rest frame) of gas near \clustername.
Note that the densest gas at the longitude of \clustername\ (vertical line) appears to be associated with the lower velocity filaments seen at lower longitudes $L_{\textrm{MS}} \lesssim 60^\circ$, which may be decelerated gas associated with the Magellanic stream.
}
\label{fig:gasspv}
\end{figure}

@@

\facility{Blanco (DECam)}
